Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-07-30 docs/comments/comments.tex
lots of shrinking, now 14 pages

\section{General Remarks}
\label{sec:rem}

We are thankful to the reviewers for their thorough reviews.
We have revised our paper based on their suggestions and comments.
All additions and changes are highlighted in yellow
in the revised manuscript.
Number wise answers to their specific
comments / suggestions / queries are as follows.

@@

\noindent
{\bf Response:}
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\

@@

In addition,
to address the comments of the 2nd and the 3rd reviewer,
we have included six more mechanisms,
thus making our study more extended.
Notably,
one of the mechanisms is presented in a recent
paper with less than 20 citations.
This increases the number of such papers
incorporated in our study (6).\\

@@

\noindent
{\bf Response:}
This is an interesting comment.
We need to mention that we did not intend to
compare the mechanisms with each other
but to highlight factors that may hinder
the widespread deployment of protection mechanisms
(we state this early on in the
``Introduction" section).

@@

\noindent
{\bf Response:}
In our study,
we observed that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
We also observed that mechanisms which
combine characteristics
from different categories,
could deal with these threats.
This indicates that when solutions
borrow elements from other categories
could be more effective.
Mechanisms can also work together
to defend against different attacks.
For instance,
developers could use {\sc csp}
and \textsc{sql}rand
together to deal with {\sc xss} and
{\sc sql} injection respectively.
We have updated Subsection 7.3
(now named ``Performance Overhead,
Deployment and Security Remarks")
to include all the above remarks.\\

@@

\noindent
{\bf Response:}
Indeed,
Cross Frame Scripting (\textsc{xfs}) attacks
are comprise a novel category worth mentioning.
We now refer to \textsc{xfs} attacks
at the end of Section 3 (``Exploitation Model").
We also provide a corresponding example.\\

>>>>

@@

\noindent
{\bf Response:}
We are thankful to the reviewers for their thorough reviews.
We have revised our paper based on their suggestions and comments.
All additions and changes are highlighted in yellow
in the revised manuscript.
Number wise answers to their specific
comments / suggestions / queries are as follows.\\

@@

In addition,
to address the comments of the second
and the third reviewer,
we have extended our study by
including six more mechanisms.
Notably,
one of the mechanisms was presented in a recent
paper with less than 20 citations.
This increases the number of such cases
in our paper (6).\\

@@

\noindent
{\bf Response:}
This is an interesting comment.
We need to mention that we did not intend to
compare the mechanisms with each other
but to analyze and categorize them,
and highlight factors that may hinder
their widespread deployment
(we state this early on in the
``Introduction" section).

@@

\noindent
{\bf Response:}
In our study,
we observed that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
We also observed that mechanisms which
combine characteristics
from different categories,
could deal with these threats.
This indicates that when solutions
borrow elements from other categories
could be more effective.
Mechanisms can also work together
to defend against different attacks.
For instance,
developers could employ both {\sc csp}
and \textsc{sql}rand
to deal with {\sc xss} and
{\sc sql} injection respectively.
We have updated Subsection 7.3
(now named ``Performance Overhead,
Deployment and Security Remarks")
to include all the above remarks.\\

@@

\noindent
{\bf Response:}
Indeed,
Cross Frame Scripting (\textsc{xfs}) attacks
comprise a novel category worth mentioning.
We now describe \textsc{xfs} attacks
in Section 3 (``Exploitation Model").
We also provide a corresponding example.\\
